---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# frstore

<!-- badges: start -->
<!-- badges: end -->

{frstore} is an `R` interface to perform the create, read, update, and delete (CRUD) operations on the Cloud Firestore database via REST API.

## Installation

You can install the development version of frstore like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```
{frstore} requires an access token to interact with the Cloud Firestore database. [{frbs}](https://github.com/kennedymwavu/frbs/tree/main) provides useful functions to sign up and sign in:

```{r signin, eval=FALSE}
library(frbs)
# Sign up via Firebase authentication:
frbs_sign_up(email = "<EMAIL>", password = "<PASSWORD>")
# Sign in:
foo <- frbs_sign_in(email = "<EMAIL>", password = "<PASSWORD>")
```

`foo$idToken` provides the access token.

## Create document(s)

Create a document without specifying data:

```{r create1, eval=FALSE}
library(frstore)
frstore_create_document("test/firstDoc", foo$idToken)
```

Create a document in a subcollection by providing the `data` argument: 

```{r create2, eval=FALSE}
data_list <- list(
  fields = list(
    age = list("integerValue" = 36),
    name = list("stringValue" = "merry")
 )
)
frstore_create_document("test/firstDoc/firstCollection/doc", foo$idToken, data_list)
```

Create a document in the main collection:

```{r create3, eval=FALSE}
frstore_create_document("test/secondDoc", foo$idToken, data_list)
```

## Read data

Get document(s) with all fields:

```{r read1, eval=FALSE}
frstore_get("test", foo$idToken)
frstore_get("test/doc", foo$idToken)
```

Get a specific field from a document:

```{r read2, eval=FALSE}
frstore_get("test/doc", foo$idToken, fields = c("age"))
```


## Update data

Suppose there is an existing document at `test/firstDoc/firstCollection/doc` and we want to update it with new data:

```{r update, eval=FALSE}
data_list <- list(
   fields = list(
     age = list("integerValue" = 3600),
     name = list("stringValue" = "merryyyy")
   )
)
frstore_patch("test/firstDoc/firstCollection/doc", foo$idToken, data_list)
```


## Delete data

Suppose there is an existing document at `test/firstDoc/firstCollection/doc` and we want to delete it:

```{r delete, eval=FALSE}
frstore_delete("test/firstDoc/firstCollection/doc", foo$idToken)
```

